Visual proteomics using whole-lamella 2D template matching

### 2022-02-25 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1899812620

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/c726b59baf4d652934928fac32dda6261f8cf435/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/c726b59baf4d652934928fac32dda6261f8cf435}{jojoelfe/deco\_lace\_template\_matching\_manuscript@c726b59}
on February 25, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0b9b63c}
on February 25, 2022.
